Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-16 write-ups/PLDI/paper.tex
Reached page limit.

\paragraph{Transmitted variables}

@@

\paragraph{Active workroups}

@@

\paragraph{Semantics for $\offerkill$}

@@

\paragraph{Semantics for $\offerfork$}

@@

Notice that $k=0$ is always a legitimate choice for the number of
workgroups to be spawned by an $\offerfork$ call, and if the number of
active workgroups $M$ is equal to the workgroup limit $N$, $k=0$ is
guaranteed.

\paragraph{Global barriers}

>>>>

\vspace{-1mm}
\paragraph{Transmitted variables}

@@

\vspace{-1mm}
\paragraph{Active workroups}

@@

\vspace{-1mm}
\paragraph{Semantics for $\offerkill$}

@@

\vspace{-1mm}
\paragraph{Semantics for $\offerfork$}

@@

Notice that $k=0$ is always a valid choice for the number of
workgroups to be spawned by $\offerfork$, and is guarateed if $M$
is equal to the workgroup limit $N$.

\vspace{-1mm}
\paragraph{Global barriers}
